Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-03-03 paper/paper.tex
sketchy thoughts on paper-arrow plot Tested everything on bennet.

\begin{figure}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \caption{Box plots of Mannik shapes for sizes at the lower stability
    threshhold.  The vertical axis shows stacked and changing over
    time the total number of proteins that are of four different
    compound stages and in the different sections of the cell.  Both
    shapes have longer axis of roughly 2.2$\mu m$.}
  \label{box-mannik}
\end{figure}

@@

\section{Our '\textgreater' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
  \label{Vbox}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
  \label{Vbox2}
\end{figure}

We have also simulated a flattened '\textgreater' shape that shows an
interesting size dependent pattern (seen in
Figures~\ref{Vbox}~and~\ref{Vbox2}).  When the shape is small enough
that the distance from the apex tip to the opposite curve is less than
our stability limit, a simple, two pole oscillation pattern develops
and is sustained (where the two poles are on opposite leftward corners
of the cell).  When the cell is increased in size so that this
distance is approximately equal to our stability value, the cell
develops a double oscillation in time, where the maxima oscillates
from the lower corner to the rightward apex, then \emph{back to the
  lower corner}, then to the apex again, then to the upper corner,
then back to the apex, then to the upper corner, then to the apex
again, then back to the lower corner, and continues this pattern
indefinately.  Figure~\ref{Vbox} shows the smaller size, for which the
protein oscillates simply, and an intermediate size, which shows a
pattern for which one out of three spikes in the regular oscillation
is less significant.  This second pattern seems to be a precursor to
the double oscillation that seen in Figure~\ref{Vbox2}.  The second
plot shown in Figure~\ref{Vbox2} shows a slightly larger cell for
which the distance measured is larger than our stability limit
distance.  This simulation shows a random pattern.

>>>>

\begin{figure}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  %\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
  %\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \caption{Box plots of Mannik shapes for sizes at the lower stability
    threshhold.  The vertical axis shows stacked and changing over
    time the total number of proteins that are of four different
    compound stages and in the different sections of the cell.  Both
    shapes have longer axis of roughly 2.2$\mu m$.}
  \label{box-mannik}
\end{figure}

@@

\section{Our '\textgreater' Shaped Cells}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
  \label{fig:Vbox}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
  \label{fig:Vbox2}
\end{figure}

We have also simulated a flattened '\textgreater' shape that shows an
interesting size dependent pattern (seen in
Figures~\ref{fig:Vbox}~and~\ref{fig:Vbox2}).  When the shape is small enough
that the distance from the apex tip to the opposite curve is less than
our stability limit, a simple, two pole oscillation pattern develops
and is sustained (where the two poles are on opposite leftward corners
of the cell).  When the cell is increased in size so that this
distance is approximately equal to our stability value, the cell
develops a double oscillation in time, where the maxima oscillates
from the lower corner to the rightward apex, then \emph{back to the
  lower corner}, then to the apex again, then to the upper corner,
then back to the apex, then to the upper corner, then to the apex
again, then back to the lower corner, and continues this pattern
indefinately.  Figure~\ref{fig:Vbox} shows the smaller size, for which the
protein oscillates simply, and an intermediate size, which shows a
pattern for which one out of three spikes in the regular oscillation
is less significant.  This second pattern seems to be a precursor to
the double oscillation that seen in Figure~\ref{fig:Vbox2}.  The second
plot shown in Figure~\ref{fig:Vbox2} shows a slightly larger cell for
which the distance measured is larger than our stability limit
distance.  This simulation shows a random pattern.
